---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GroceryStoreHamiltonData

<!-- badges: start -->
<!-- badges: end -->

This package is an activity completed by [Zehui Yin](https://zehuiyin.github.io/) for the course [GEOG 712 Reproducible Research Workflow with GitHub and R](https://academiccalendars.romcmaster.ca/preview_course.php?catoid=55&coid=274877), taught by [Dr. Antonio Paez](https://experts.mcmaster.ca/display/paezha) in Fall 2024.

It includes the data for the paper titled "[Food Deserts or Food Oases? Predicting Grocery Store Locations in Hamilton, Ontario](https://github.com/zehuiyin/grocery_store_hamilton)," which is the final project for the course.

## Installation

You can install the development version of `GroceryStoreHamiltonData` from [GitHub](https://github.com) with:

``` r
if(!require(remotes)){
    install.packages("remotes")
    library(remotes)
}
remotes::install_github("zehuiyin/GroceryStoreHamiltonData")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(GroceryStoreHamiltonData)
```

Load and plot the `grocery_CT` vector data. This dataset includes the geYometry of all the census tracts in Hamilton and contains a variable that shows the count of grocery stores in each census tract.

```{r}
data("grocery_DA")
hist(grocery_DA$Freq,
     main = "Grocery Store Count of Census Dissemination Area in Hamilton",
     xlab = "Grocery Store Count")
```

# How to cite

Yin, Z. (2024). GroceryStoreHamiltonData: Data for the paper "Food Deserts or Food Oases? Predicting Grocery Store Locations in Hamilton, Ontario". https://github.com/zehuiyin/GroceryStoreHamiltonData

``` latex
@Manual{GroceryStoreHamiltonData,
  title = {GroceryStoreHamiltonData: Data for the paper "Food Deserts or Food Oases? Predicting Grocery Store Locations in Hamilton, Ontario"},
  author = {Zehui Yin},
  year = {2024},
  note = {R package version 1.0},
  url = {https://github.com/zehuiyin/GroceryStoreHamiltonData}
}
```
