---
title: "Grocery Stores in Census Tracts Preparation"
---

# Code to prepare `grovery_CT` dataset goes here

```{r}
library(sf)
```

Read in two geojson files: `hamilton_CT.geojson` and `grocery.geojsonn` in the `data-raw` folder. They contains the census tracts in Hamilton and grocery stores in and near Hamilton, respectively.

```{r}
ct <- st_read("./hamilton_CT.geojson")
grocery <- st_read("./grocery.geojson")
```

Convert grocery store polygons into points.

```{r}
grocery <- st_centroid(grocery)
```

Intersect the census tract with the grocery stores.

```{r}
inter <- st_intersection(ct, grocery)
```

Count the number of grocery stores in each census tract in Hamilton.

```{r}
count <- table(inter$GeoUID) |> as.data.frame()
```

Join it to the census tract raw data.

```{r}
grocery_CT_raw <- merge(x = ct, y = count,
                        by.x = "GeoUID",
                        by.y = "Var1",
                        all.x = T)
```

```{r}
grocery_CT <- grocery_CT_raw[, c("GeoUID", 
                                 "v_CA21_1..Population..2021", 
                                 "Freq")]

grocery_CT$Freq[is.na(grocery_CT$Freq)] <- 0
```

```{r}
colnames(grocery_CT) <- c("GEOUID", "POP21", "Grocery", "geometry")
```

Save it to the data folder as `grocery_CT.rda`.

```{r}
usethis::use_data(grocery_CT, overwrite = TRUE)
```
