---
title: "Grocery Stores in Census Tracts Preparation"
---

# Code to prepare `grovery_CT` dataset goes here

```{r}
library(sf)
library(dplyr)
```

Read in two geojson files: `hamilton_DA.geojson` and `grocery.geojsonn` in the `data-raw` folder. They contains the census tracts in Hamilton and grocery stores in and near Hamilton, respectively.

```{r}
ct <- st_read("./hamilton_DA.geojson")
grocery <- st_read("./grocery.geojson")
```

Convert grocery store polygons into points.

```{r}
grocery <- st_centroid(grocery)
```

Intersect the census tract with the grocery stores.

```{r}
inter <- st_intersection(ct, grocery)
```

Count the number of grocery stores in each census tract in Hamilton.

```{r}
count <- table(inter$GeoUID) |> as.data.frame()
```

Join it to the census tract raw data.

```{r}
grocery_DA_raw <- merge(x = ct, y = count,
                        by.x = "GeoUID",
                        by.y = "Var1",
                        all.x = T)
```

```{r}
grocery_DA <- grocery_DA_raw |> select("GeoUID", 
                                       starts_with("v_CA21"), 
                                       "Freq")

grocery_DA$Freq[is.na(grocery_DA$Freq)] <- 0
```

Save it to the data folder as `grocery_CT.rda`.

```{r}
usethis::use_data(grocery_DA, overwrite = TRUE)
```
