---
title: "geog712package-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{geog712package-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Load packages

*sf* package is used to handle vector spatial data.

```{r setup}
library(geog712package)
library(sf)
```

# `grocery_CT` data

Load and plot `grocery_CT` vector data. The data contains the geometry of all the census tracts in Hamilton and have two variables showing the population count in 2021 and the grocery store counts in that census tract.

```{r}
data("grocery_CT")
plot(grocery_CT[ ,"POP21"],
     main = "2021 Population Count")
plot(grocery_CT[ ,"Grocery"],
     main = "Grocery Store Count")
```

## A simple OLS Multiple regression of these two variables

```{r}
lm1 <- lm(Grocery ~ POP21, data = grocery_CT)
summary(lm1)
```

Based on this simple regression (p-value=0.66>0.05), population count is not helpful when predicting the count of grocery stores in Hamilton.
