---
title: "GroceryStoreHamiltonData-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{geog712package-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Load packages

The *sf* package is used to handle vector spatial data.

```{r setup}
library(GroceryStoreHamiltonData)
library(sf)
```

# `grocery_DA` data

Load and plot the `grocery_DA` vector data. This dataset contains the geometry of all the census tracts in Hamilton and includes two variables: the population count in 2021 and the grocery store counts in each census tract.

```{r}
data("grocery_DA")
plot(grocery_DA[ ,"v_CA21_1..Population..2021"],
     main = "2021 Population Count")
plot(grocery_DA[ ,"Freq"],
     main = "Grocery Store Count")
```

## An OLS simple linear regression of these two variables

```{r}
lm1 <- lm(Freq ~ v_CA21_1..Population..2021, data = grocery_DA)
summary(lm1)
```

Based on this simple regression (p-value = 0.06 > 0.05), the population count is not a significant predictor of the grocery store count in Hamilton.
